\section{Future Work}\label{sec:future-work}
This project is currently a prototype suitable for development and testing environments.
Future iterations should aim to harden the implementation for production use.
While the focus has primarily been on the MLOps workflow, several areas remain to be improved:

\begin{itemize}
    \item Production-Ready Infrastructure: The current setup lacks some of the considerations and robustness needed for a mature DevOps environment.
    \item Secret Management: Integrating a dedicated secrets manager such as HashiCorp Vault would enhance security and secret handling.
    \item Improved ArgoCD Usage: While we adopted the app-of-apps pattern in ArgoCD, enabling ApplicationSets could provide better self-service capabilities for development teams and simplify multi-environment management.
    \item Pipeline Orchestration Simplification: Currently, we use three different orchestrators.
    However, as platforms evolve—GitHub introducing a model registry, Kubeflow expanding its data management capabilities, and Airflow moving toward deeper MLOps integration—it may become feasible to consolidate to a single orchestrator in the future.
    \item Repository Naming: Standardizing and renaming Git repositories to clearer, more meaningful names will improve maintainability and team onboarding.
\end{itemize}

These improvements will help transition our prototype into a scalable, production-grade MLOps-GitOps solution.
% \url{https://argo-cd.readthedocs.io/en/stable/operator-manual/applicationset/Use-Cases/#use-case-self-service-of-argo-cd-applications-on-multitenant-clusters}.
%\url{https://argo-cd.readthedocs.io/en/stable/operator-manual/secret-management/}.