\section{Acknowledgements}
I would like to express my sincere gratitude to all those who contributed to the successful completion of this thesis.
First and foremost, I extend my deepest appreciation to my thesis supervisor(s) [Name(s)] for their invaluable guidance, continuous support, and expertise throughout this research project.
Their insights into Machine Learning Develpment and practical feedback were instrumental in shaping the direction and quality of this work.
I am grateful to the team behind the LSFB (Langue des Signes de Belgique Francophone) project for providing access to their dataset.
Their collaboration was essential in demonstrating the real-world applicability of our MLOps-GitOps workflow, and their domain expertise greatly enriched the practical validation of our implementation.
Special thanks to my fellow students and peers who provided valuable feedback during the development process, particularly regarding the integration of GitOps methodology with our MLOps workflow.
Their suggestions and collaborative discussions helped refine our approach and improve the overall solution.
I would also like to acknowledge the open-source community and the developers of the various tools and frameworks that made this implementation possible, including Kubernetes, Docker, Helm, Airflow, and Kubeflow.
The extensive documentation and community support for these technologies were important resources throughout the development process.
Finally, I am grateful to my family and friends for their unwavering support and encouragement throughout my master's program and the completion of this thesis project.
This research would not have been possible without the collective contributions of all these individuals and communities.