\chapter*{Prologue} %Exordium, Prelude, Introduction

\section*{Introduction}

Software development has changed a lot over the years, moving from manual steps to automated workflows.
Old methods had long manual separate steps, often causing problems.
To deliver faster and improve quality modern development has shifted to automation.
Machine Learning development also moves towards more automation\cite{Haakman2021}.

According to\cite{10.1145/3533378}, only a small percentage of machine learning projects successfully reach production deployment, due to issues and operational complexity\cite{Haakman2021}.
The emergence of MLOps as a distinct discipline represents a response to these challenges, offering structured approaches to model development, deployment, monitoring, and governance\cite{treveil2020introducing}.
This thesis begins with a comprehensive state-of-the-art review of MLOps methodologies, frameworks, and tools currently employed across industry and research domains.
Our review is motivated by the need to establish a solid theoretical and practical foundation for developing a flexible MLOps workflow that can address the diverse requirements of modern enterprises and research organizations.
We aim to identify in the literature the core components and principles that constitute effective MLOps implementations\cite{DBLP:journals/corr/abs-2103-08942}.

The insights gained from this review directly inform our subsequent implementation project, where we develop a modular, adaptable MLOps workflow designed to accommodate various scales of machine learning projects.
Our implementation strategy follows a two-phase approach: first, we develop and validate our workflow using a controlled demonstration model that shows core functionality in a simplified context.
This allows us to establish baseline capabilities and verify fundamental workflow mechanics without the complexities of a production system.
Following this initial validation, we demonstrate the workflow's flexibility and robustness by applying it to a real-world production system—the LSFB (Langue des Signes de Belgique Francophone) model developed at our university\cite{9534336}.
By adapting our workflow to enhance this existing system, we provide tangible evidence of its practical utility and adaptability.

\input{chapters/intro/acknowledgement}
